---
title: "Vignette in package TextMining"
author: "Yahui Zhang, Yi Xu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## Introduction
## 1.Data
This package is concerned with Book content analysis. To get book resource, you can go to https://www.gutenberg.org and search for the book you want. You don't need to download the digital form of book, but find "EBook-No." of the book and gutenberg_download(EBook-No.) can help download book data into R. There can be many editions of one book, but EBook-No can identify them, for example, the EBook-No.1342 associated with only one result of 'Pride and Prejudice'.


## 2.Funcitons

### 2.1 Term Frequency Analysis

### wf_hist(x)
It is used to make a histogram for the 10 most frequent words in the book. 
x is the book data.


### 2.2 Word Cloud

### wcloud(x)
It is used to make a wordcloud for the 200 most frequent words in the book. 
x is the book data.



### 2.3 Word Bigram

### bitable(x,y)
It is used to find bigrams of a specific word in this book.
x is the book data, y can be either a list of character names such as c("Jane","Ben","Elizabeth") or a single name.



### 2.4 Word Relationship Analysis

### binet(x)
It is used to show the network of bigrams in the book.
x is the book data.


### 2.5 Appearance Summary

### AppearCount(x,y)
It is used to show a dataframe for appearance times of character in each chapter.
x is the book data, y is character name.



### 2.6 Sentiment Analysis

### Emo(x,y)
It is used to make a histogram for main sentiment of each chapter in the book.
x is the book data, y is character name.



```{r, echo=FALSE}
knitr::opts_chunk$set(purl = FALSE)
```

